Geophysicists should use the gravity disturbance rather than the gravity anomaly

### 2018-05-18 manuscript/letter.tex
If we're gonna be provocative, start with the title
Simplify the abstract and add a solution to the end

\title[Gravity anomaly or gravity disturbance?]
      {Should geophysicists use gravity anomaly or gravity disturbance?}

@@

\begin{summary}
 In applied geophysics, the gravity anomaly has long been used for representing the
 gravitational effect produced by gravity sources, which are defined as the density
 contrasts between the internal density distribution of the Earth and the normal Earth.
 The gravity anomaly is defined by the difference between the gravity (produced by the
 Earth) on the Geoid and the normal gravity (produced by the normal Earth)
 on reference ellipsoid, both at the same geodetic latitude and longitude.
 Because these quantities are not defined at the same point,
 the gravity anomaly does not represent the gravitational effect due to the gravity
 sources and, consequently, cannot be considered a harmonic function.
 On the contrary, the gravity disturbance is defined by the difference between
 the gravity and normal gravity at the same point. Consequently, the centrifugal
 effects can be neglected, the gravity disturbance can be considered a harmonic
 function representing the gravitational effect due to the gravity sources and then
 it satisfies the premise behind most of the processing techniques of potential-field
 data (e.g., upward/downward continuations). Then, rigorously, the gravity disturbance
 is  more appropriated to be used for estimating density variations in subsurface.
 The use the gravity anomaly for most of the geophysicists carries the
 implicit meaning that it can be considered a good approximation of the gravity
 disturbance. It is important to bear in mind, however, that in Brazil, for example,
 the maximum absolute difference between the gravity disturbance (on or close
 to the Earth’s surface) and the Free-air anomaly reaches 9.3 mGal.

\end{summary}

>>>>

\title[Gravity anomaly or gravity disturbance?]
      {Geophysicists should use the gravity disturbance rather than the gravity anomaly}

@@

\begin{summary}
 The gravity anomaly is defined as the difference between the Earth's gravity
 on the geoid and the gravity of the normal Earth on the reference ellipsoid.
 Because these quantities are not at the same point, the anomaly contains
 centrifugal accelerations and cannot be considered a harmonic function.
 The gravity disturbance is the difference between gravity and normal gravity
 at the same point.
 Consequently, the centrifugal effects can be neglected and the disturbance can
 be considered a harmonic function.
 This is the premise behind most potential-field data processing techniques
 (e.g., upward/downward continuation and vertical derivatives).
 Unlike the anomaly, the disturbance is due solely to the
 gravitational effects of geologic sources, making it the most appropriate
 choice for modelling.
 Use of the gravity anomaly in geophysics carries with it the implicit
 assumption that it is a good approximation for the gravity disturbance.
 However, bear in mind that the difference between the gravity disturbance and
 the free-air anomaly can be larger than 10 mGal worldwide.
 Fortunately, the solution to these problems is to simply replace
 heights referenced to the geoid (orthometric) with heights referenced to the
 ellipsoid (geometric) for geophysical use cases.
\end{summary}
